\chapter{Introduksjon}
\setlength{\parindent}{2ex}
The purpose of this document is to clarify for the we in the development team and our customers, Ovase, what kind of functionality and qualities the knowledge based information system Ovase.no shall contain. Ovase.no will henceforth in this document be referred to as just "the system". In this document, the reader will gain insight into the functional and non-functional requirements the implementation of the system eventually shal fulfill. The document also describes the quality requirements that the system must meet, the technical and experience-related constraints on its development, and any COTS components used to develop the system. \par
On the 23rd of August a group of seven students at NTNU received was assigned the continued development of the Ovase web application as their assignment in TDT4290 Kundestyrt Prosjekt. The customer contact from whom requirments and use cases were elicited are Anine Drageset and Peder Langdel, two fifth year students who developed the first version of the system as a wiki only. The group's assignment is to expand the web page with two modules intended to be implemented separately. The development process has been planned during week 35, and runs over a time period of eight weeks, divided into four sprints of equal length of time. A final report documenting all of the four sprints as well as the final implemented architecture is to be delivered by the 16th of November 2016. \par
This document is subject to change during the span of project.


